### 2020-12-08 rebuttal.txt

----------------------- REVIEW 1 ---------------------

> The key elements of the type system, particularly the annotations in arrow types, the shape of typing judgments, the typing of communication primitives, are basically taken from [37]. The authors also move away from a calculus strictly justified by logic, e.g. by resorting to traditional process-algebraic structural congruence and reduction relations, and they work with a hybrid form of (partially encoded) session types. Overall, I see a substantial overlap between this paper and [37], which somehow lessens the depth of the contribution.

> I appreciate the effort made by the authors of tackling an example from the bibliography (Milner's cyclic scheduler), but I'm not convinced that presenting that particular example alone, without even trying to showcase a typing derivation, is an effective strategy. I gained more insights about the key aspects of the typing discipline by looking at [37], in which many (small) examples are used to illustrate the type system.

* Otherwise, the paper is technically sound as far as I checked, it is well-written and quite accessible.

In summary, this is a fine paper that continues an established investigation on the use of priorities for enabling a more flexible use of session channels, but it lacks a particularly compelling message to convey.

## On the choice of the example(s)

As presented, Example 1 (also the PCP version) is ill-typed and, I think, not self contained. Note that d is used while d' is not and there is a restriction for d and d'. I think a wait d' is missing somewhere, possibly next to proc‚ÇÅ if I interpret the diagram in the Appendix correctly.

> Also, I don't understand what M_i and N_i are (similarly for P_i and Q_i in the PCP version of the example). Maybe the authors imply that the actual system is more complex that the one shown here, where M_i and N_i contain unspecified parts of the system. However, I think that the example is already more complex than necessary, and that it would be fine to simply state that all that matters is the communication structure being modeled.

That’s exactly what they’re meant to convey, yes.

> Speaking of complexity, the case for PGV can be made by considering
>
>  	(aa')(bb') (close a; wait b' || wait a'; close b)
>
> which is a streamlined version of the example in which there are just two processes connected by two sessions. This is the essential configuration that cannot be modeled by the calculi strictly based on linear logic, since the two threads share two channels. Yet, this configuration is well typed in the presented type system and therefore is deadlock free.
>
> This example is simple enough that a full typing derivation can be shown in the paper, possibly at the expense of the few proof sketched which can be moved in the appendix anyway.

That’s probably a good call.

> At the same time, the example given by the authors does not make use of any interesting function (apart from the constants wait and close) and therefore it fails to illustrate the relevance of annotations on arrow types.

We should probably add an example which uses closures.

> I presume there are side conditions in SC-RESCOMM requiring that {z,w} \cap {x,y} = \emptyset.
> I presume there are side conditions in E-NEW requiring that x,y do not occur free in F

Yes, to both.

> The encoding from PCP to PGV is routine and does not reveal particularly challenging or surprising aspects given the expressiveness of PGV. In fact, I suspect it can be further simplified (at least in its presentation) by considering only the encoding into the functional fragment of PGV. Clearly the translation to configurations deals with a subset of cases compared to the translation to terms. I wonder if it's possible to *present* the second translation only, which alone is complete as far as the encoding goes.

Such a translation would be complete, but not sound.

----------------------- REVIEW 2 ---------------------

The paper fits well the scope of FOSSACS.

> Counter-examples, i.e., deadlocking processes that cannot be typed, such as dining philosophers.

Yes.

> At least one example demonstrating the interaction between higher order and deadlock-freedom, i.e., an example in which a function is sent and applied and where the actions present in the function's body are controlled by the latent effect of the arrow type.

Yes.

----------------------- REVIEW 3 ---------------------

> As a non-expert reviewing the paper, my main concern is the amount of novel technical content: the technique in use has been developed by one of the authors in the context of a process calculus and is adapted here to a known linear concurrent λ-calculus. This would not be an issue if the attempt exposed some technical difficulties in adapting the technique to the setting of GV or uncovered some important insights; however, this does not seem to be the case. Thus, from the perspective of a non-expert, this paper seems to be too closely related to prior work to warrant an acceptance recommendation. Still, particularly as a non-expert, I would welcome any comments that would highlight the significance of technical contributions of the paper, and if so, would be happy to adjust my assessment.

### 2020-12-08 rebuttal.txt

TODO:

- a word of thanks;
- acknowledge the lack of examples, and commit to addressing that;
- clarify our contribution: priority gv is the first session-typed functional language which with priorities and strong ties to linear logic via its correspondence with PCP and its relation to the original CP and GV languages;

### 2020-12-09 rebuttal.txt

We thank the reviewers for their thorough reviews and very useful feedback.

First of all, we acknowledge the lack of examples and we commit to adding them. We will illustrate PGV with further well-typed programs together with type derivation; and deadlocked programs (including the example by Reviewer 1).

The reason for including cyclic scheduler was deliberately to connect our work to the previous FoSSaCS work on PCP. We wanted to show how the well-known Milner's scheduler can be written in PGV (for the first time) and use it to illustrate our encoding of PGV to PCP, thus closing this circle.

We will clarify our contributions in the introduction. Summing them up here: PGV is the first session-typed functional language with priorities *and* strong ties to linear logic via its correspondence with PCP and its relation to the CP and GV languages.

### 2020-12-09 rebuttal.txt

We thank the reviewers for their thorough reviews and very useful feedback, which we'll address as follows.

First of all, we acknowledge the lack of examples and we commit to adding them to the (potential) final version.
We will illustrate PGV by adding examples for each of the following:
-- deadlock-free processes (including the streamlined version with two processes connected by two sessions, suggested by Reviewer 1) together with their typing derivations;
-- deadlocked processes that cannot be typed, thus illustrating how priorities work, suggested by Reviewers 1 and 2;
-- processes which use closures, thus illustrating the relevance of annotations on arrow types, suggested by Reviewer 1;
-- processes demonstrating the interaction between higher order and deadlock freedom, suggested by Reviewer 2.

Regarding the cyclic scheduler, we included it to deliberately connect our work to the previous FoSSaCS work on PCP. We wanted to show how the well-known Milner's scheduler can be written in PGV (for the first time) and use it to illustrate our encoding of PCP to PGV, thus closing this circle on the cyclic scheduler. We will make this clearer in the paper.

Regarding our contributions, we will highlight them better in the introduction.
Summing them up here: PGV is the first session-typed functional language with priorities *and* strong ties to linear logic via its correspondence with PCP and its relation to the CP and GV languages.

Lastly, we will implement all minor comments by all reviewers, thanks for pointing them out.

----------------------- REVIEW 1 ---------------------
Regarding the overlap with [37] we would like to mention that our work was developed completely independently of [37] as the authors came to know this work only during the writing up of the paper while working on related works.
We still want to emphasise the differences between our work and [37]: i) our work has strong ties to logic, hence why we also present the encoding PGV->PCP; ii) COMPLETE... 
We will state the above clearly in the paper.

> As presented, Example 1 (also the PCP version) is ill-typed and, I think, not self contained. Note that d is used while d' is not and there is a restriction for d and d'. I think a wait d' is missing somewhere, possibly next to proc₁ if I interpret the diagram in the Appendix correctly.

Regarding M_i and N_i in the PCP cyclic scheduler, the reviewer understood this correctly and we will simply state that what matters is the communication structure being modelled.

Regarding the encoding of PCP to PGV and presenting only the encoding to the functional fragment, we have thought about this too. However, such encoding is complete but not sound. The reason being...

Minor:

Regarding side conditions in SC-RESCOMM and E-NEW, the reviewer is right and we will add them.

Regarding T-VAR and T-CONST we will mention your suggestion.

@@

----------------------- REVIEW 2 ---------------------

As mentioned at the top, we will add more examples to the paper.

Regarding the presentation of the main sections: we will explain more in detail how priorities work, especially with the aid of the aforementioned examples. We will systematise the the prevention of CP, PCP, GV and PGV, by dedicating subsections to each of them before diving into the details of our work.

Regarding our contribution, we will make them clearer for non-experts by first illustrating the use and benefits of GV and then the benefits of splitting new and spawn in PGV and its ties to logic (this will relate to the CP,PCP,GV,PGV explanations above).

@@

----------------------- REVIEW 3 ---------------------

We will clarify the contributions better, this was also suggested by other reviewers.

It is true that priorities are not new and they were already used in PCP, which is a process calculus ties to logic. However, PGV is the first functional calculus with priorities that also ties to logic as PCP.

We are in fact making this connection to linear logic explicit by defining a sound encoding of PCP to PGV. Furthermore, as a case study for PGV and the encoding, we deliberately chose Milner's cyclic scheduler presented in PCP previously. The reason for this choice is to show how a process in the literature of PCP can be translated using our encoding into PGV.

However, in addition to the cyclic scheduler, we will add the examples mentioned at the top of this letter to better illustrate PGV and its type system.

### 2020-12-09 rebuttal.txt

We thank the reviewers for their thorough reviews and very useful feedback, which we'll address as follows.

First of all, we acknowledge the lack of examples and we commit to adding them to the potential final version.
We will illustrate PGV by adding examples for each of the following:

  - deadlock-free processes—including the streamlined version with two processes connected by two sessions, suggested by Reviewer 1—together with their typing derivations;
  - deadlocked processes that cannot be typed, thus illustrating how priorities work, suggested by Reviewers 1 and 2;
  - processes which use closures, thus illustrating the relevance of annotations on arrow types, suggested by Reviewer 1;
  - processes demonstrating the interaction between higher order and deadlock freedom, suggested by Reviewer 2.

@@

Regarding the cyclic scheduler, we included it to deliberately connect our work to the previous FoSSaCS work on PCP.
We wanted to show how the well-known Milner's scheduler can be written in PGV (for the first time) and use it to illustrate our encoding of PCP to PGV, thus closing this circle on the cyclic scheduler.
We will make this clearer in the paper.

Regarding our contributions, we will highlight them better in the introduction. Summing them up here:
  - PGV is the first session-typed functional language with priorities *and* strong ties to linear logic via its correspondence with PCP and its relation to the CP and GV languages.
  - PGV addresses several problems in the original GV language, most notably:
    * our version does not have the pseudo-type S^#; and
    * our structural congruence is type preserving.

@@

Lastly, we will implement all minor comments by all reviewers, thanks for pointing them out.

----------------------- REVIEW 1 ---------------------
Regarding the overlap with [37] we would like to mention that our work was developed completely independently of [37] as the authors came to know this work only during the writing up of the paper while working on related works.
We still want to emphasise the differences between our work and [37]:

  - PGV has a clear correspondence with a process calculus, PCP;
  - PGV has strong ties to linear logic, via its correspondence to PCP and its transitive relation to CP;

We will state the above clearly in the paper.

> As presented, Example 1 (also the PCP version) is ill-typed and, I think, not self contained.
> Note that d is used while d' is not and there is a restriction for d and d'.
> I think a `wait d'` is missing somewhere, possibly next to proc_1 if I interpret the diagram in the Appendix correctly.

Regarding M_i and N_i in the PCP cyclic scheduler, the reviewer understood this correctly and we will simply state that what matters is the communication structure being modelled. The missing `wait d'` should be in N_1, as the reviewer correctly inferred. We will mention this clearly in the paper.

Regarding the encoding of PCP to PGV and presenting only the encoding to the functional fragment, we have thought about this too. Such an encoding is complete but not sound, as the translation to configurations does some evaluation of top-level new/spawn constructs. For instance, the process ‘x[y].P’ has no reductions. Similarly, its translation to a configuration has no reductions. However, its translation to a term, ‘o let (y,z) = new in let x = send (z,x) in ((P))_M’ can reduce to ‘(vyz)(o let x = send (z,x) in ((P))_M)’.

### 2020-12-09 rebuttal.txt

We thank the reviewers for their thorough reviews and very useful feedback, which we'll address as follows.

First of all, we acknowledge the lack of examples and we commit to adding them to the potential final version.
We will illustrate PGV by adding examples for each of the following:

  - deadlock-free processes—including the streamlined version with two processes connected by two sessions, suggested by Reviewer 1—together with their typing derivations;
  - deadlocked processes that cannot be typed, thus illustrating how priorities work, suggested by Reviewers 1 and 2;
  - processes which use closures, thus illustrating the relevance of annotations on arrow types, suggested by Reviewer 1;
  - processes demonstrating the interaction between higher order and deadlock freedom, suggested by Reviewer 2.

Regarding the cyclic scheduler, we included it to deliberately connect our work to the previous FoSSaCS work on PCP where the cyclic scheduler was originally presented as an example of a deadlock-free process not typable in CP.
In our work, we wanted to show how the well-known Milner's scheduler can be written in PGV-for the first time-and use it to illustrate our encoding from PCP to PGV, thus closing the circle on the cyclic scheduler example.
We will make this more explicit in the paper.

Regarding our contributions, we will highlight them better in the introduction. Summing them up here:
  1. PGV is the first session-typed functional language with priorities *and* strong ties to linear logic via its correspondence with PCP and its relation to the CP and GV languages.
  2. PGV addresses several problems in the original GV language, most notably:
    a. our version does not have the pseudo-type S^#; and
    b. our structural congruence is type preserving.
  3. The connection of PGV to logic is given via a sound and complete encoding of PCP to PGV and showcase it with the encoding of cyclic scheduler to PGV.

We would like to draw attention to a. and b. above.
Previous work on GV does not satisfy a. and the pseudo-type S^# is explicitly included in the type language, but then explicitly excluded in all the typing rules where only "concrete" types, like (input) ?S or (output) !S can be used. Consequently, the technical presentation is cumbersome in original GV. Another major issue with GV is that structural congruence is not type preserving. Consequently, in order to prove the main results in GV, one would first need to prove that: any ill-typed term which is obtained via structural congruence (or reduction) starting from a well-typed term, can be rewritten into a well-typed term. In our work, the type preserving structural congruence makes the presentation cleaner and more elegant and aligns for example with structural congruence in process calculi.

Lastly, we will implement all "minor comments" by all reviewers, thanks for pointing them out.

----------------------- REVIEW 1 ---------------------
Regarding the overlap with [37] we would like to point out that our work was developed completely independently of [37]. The authors were not aware of[37] until working on the related work of this paper.
We still want to emphasise the differences between our work and [37], which we will also state in the paper:

@@

  - PGV has a clear correspondence with a process calculus, PCP;
  - PGV has strong ties to linear logic, via its correspondence to PCP and its transitive relation to CP;

Regarding M_i and N_i in the PCP cyclic scheduler, the reviewer understood this correctly and we will simply state that what matters is the communication structure being modelled.
The missing `wait d'` should be in N_1, as the reviewer correctly inferred. Moreover, with this change the process is well typed. We will clarify this in the paper.

@@

Regarding side conditions in SC-RESCOMM and E-NEW, the reviewer is right and we will add them.

Regarding T-VAR and T-CONST we will mention your suggestion. Thanks

----------------------- REVIEW 2 ---------------------

As mentioned at the top of this letter, we will add more examples in the paper.

Regarding the presentation of the main sections: we will explain more in detail how priorities work, especially with the aid of the aforementioned examples. We will systematise the prevention of CP, PCP, GV and PGV, by dedicating subsections to each of them before diving into the details of our work.

Regarding our contribution, we will make them clearer for non-experts, which we summarised at the top of the letter. We will illustrate the use and benefits of GV and then the benefits of splitting new and spawn in PGV and its ties to logic (this will relate to the CP,PCP,GV,PGV explanations that we will add).

@@

----------------------- REVIEW 3 ---------------------

We will clarify the contributions better, this was also suggested by other reviewers and we summarised them at the top.

A key contribution of our work is the connection of PGV with logic, which we make explicit by defining a sound and complete encoding of PCP to PGV. Furthermore, as a case study for PGV and the encoding, we deliberately chose Milner's cyclic scheduler presented in PCP.

As mentioned, in addition to the cyclic scheduler, we will add the examples at the top of this letter to better illustrate PGV and its type system.

### 2020-12-09 rebuttal.txt

We would like to draw attention to a. and b. above.
Previous work on GV does not satisfy a. and the pseudo-type S^# is explicitly included in the type language, but then explicitly excluded in all the typing rules where only "concrete" types, like (input) ?S or (output) !S can be used. Consequently, the technical presentation is cumbersome in original GV. Another major issue with GV is that structural congruence is not type preserving. Consequently, in order to prove the main results in GV, one would first need to prove that: any ill-typed term which is obtained via structural congruence (or reduction) starting from a well-typed term, can be rewritten into a well-typed term. In our work, the type preserving structural congruence makes the presentation cleaner and more elegant and aligns for example with structural congruence in process calculi.

Lastly, we will implement all "minor comments" by all reviewers, thanks for pointing them out.

----------------------- REVIEW 1 ---------------------
Regarding the overlap with [37] we would like to point out that our work was developed completely independently of [37]. The authors were not aware of[37] until working on the related work of this paper.
We still want to emphasise the differences between our work and [37], which we will also state in the paper:

  - PGV has a clear correspondence with a *process calculus*, PCP;
  - PGV has strong ties to *linear logic*, via its correspondence to PCP and its transitive relation to CP;

### 2020-12-10 rebuttal.txt

Regarding our contributions, we will highlight them better in the introduction. Summing them up here:
  1. PGV is the first session-typed functional language with priorities *and* strong ties to linear logic via its correspondence with PCP and its relation to the CP and GV languages.
  2. PGV addresses several problems in the original GV language, most notably:
     a. our version does not have the pseudo-type S^#; and
     b. our structural congruence is type preserving.
  3. The connection of PGV to logic is given via a sound and complete encoding of PCP to PGV and showcase it with the encoding of cyclic scheduler to PGV.

We would like to draw attention to a. and b. above.
Previous work on GV does not satisfy a. and the pseudo-type S^# is explicitly included in the type language, but then explicitly excluded in all the typing rules where only "concrete" types, like (input) ?S or (output) !S can be used. Consequently, the technical presentation is cumbersome in original GV. Another major issue with GV is that structural congruence is not type preserving. Consequently, in order to prove the main results in GV, one would first need to prove that: any ill-typed term which is obtained via structural congruence (or reduction) starting from a well-typed term, can be rewritten into a well-typed term. In our work, the type preserving structural congruence makes the presentation cleaner and more elegant and aligns for example with structural congruence in process calculi.

Lastly, we will implement all "minor comments" by all reviewers, thanks for pointing them out.

----------------------- REVIEW 1 ---------------------

Regarding the overlap with [37] we would like to point out that our work was developed completely independently of [37]. The authors were not aware of[37] until working on the related work of this paper.
We still want to emphasise the differences between our work and [37], which we will also state in the paper. PGV stems from GV differently from [37] and:

### 2021-01-05 introduction.tex
Processed minor comments and inserted unresolved comments as todo notes.

\begin{document}
\section{Introduction}
Communication and concurrency are at the basis of our modern society. Every service or device we interact with, from smart phones, to health monitors or any other IoT device, relies on communication. Hence, verification of communication in concurrent settings is important for our own safety. Session types are a type formalism which can be used to specify and verify communication protocols between two or more communicating agents~\cite{honda93,takeuchihonda94,hondavasconcelos98,carbonehonda07}.
Session types have been studied for many programming paradigms, but to date the most successful settings remain the $\pi$-calculus~\cite{sangiorgiwalker01}---a process calculus for communication and concurrency, and Good Variation (GV)~\cite{wadler15,lindleymorris15}---a linear concurrent $\lambda$-calculus.
Session-typed concurrent $\lambda$-calculus and $\pi$-calculus satisfy communication safety and session fidelity, namely that communication proceeds without any type mismatch of the data being transmitted and follows the predefined protocol specified by a session type.
Another key property in a concurrent setting is deadlock freedom, stating that agents communicate without getting stuck in cyclic dependencies. Unfortunately, deadlock freedom is a more involving property and session types alone are not enough to rule out deadlocks in cyclic structures of multiple interleaved sessions. Several techniques have been developed to address deadlock freedom in the $\pi$-calculus and concurrent $\lambda$-calculus with session types.

@@

With regards to GV, the original work on session types in GV~\cite{gayvasconcelos10,gayvasconcelos12} did not satisfy deadlock freedom. Later on, calculi in the GV family~\cite{wadler15,lindleymorris15} have achieved deadlock freedom via a syntactic restriction, \ie by combining channel creation and thread spawning into a single operation, called fork. The fork construct is the term representation of the cut construct in CP, which evaluates to a channel restriction combined with a parallel composition. Unfortunately, as with CP, this is restrictive as it limits communication structures to trees. There are several benefits of working with a functional language as opposed to process calculi. Functional languages support higher-order functions, and have a capability for abstraction not usually present in process calculi. Working within a functional language allows to derive extensions of the communication capabilities of the language via well-understood extensions of the functional fragment, \ie deriving internal/external choice via sum types. Finally, in concurrent functional calculi, there is a clear separation between a program that the user writes, and a configuration, which is the state of a system as it evaluates. In process calculi, these are conflated.
Moreover, the benefit of working with GV over other session-typed functional languages is that GV has strong ties to linear logic, via its relation to CP~\cite{wadler12}, and consequently it has strong formal properties, \eg deadlock freedom, albeit in a restrictive way.
Following the above observations, we aim to further investigate GV and deadlock freedom, and thus we pose our research question:

>>>>

\begin{document}
\section{Introduction}
\todo{The first three sentences of the introduction are too general to motivate the paper and feel a bit out of place. Consider removing them.}
Communication and concurrency are at the basis of our modern society. Every service or device we interact with, from smart phones, to health monitors or any other IoT device, relies on communication. Hence, verification of communication in concurrent settings is important for our own safety. Session types are a type formalism which can be used to specify and verify communication protocols between two or more communicating agents~\cite{honda93,takeuchihonda94,hondavasconcelos98,carbonehonda07}.
\todo{These two settings are very different. The $\pi$-calculus is a mobile process algebra preceding inside which session types were developed and GV is an ad-hoc calculus made to demonstrate how propositions can be used as types.}
Session types have been studied for many programming paradigms, but to date the most successful settings remain the $\pi$-calculus~\cite{sangiorgiwalker01}---a process calculus for communication and concurrency, and Good Variation (GV)~\cite{wadler15,lindleymorris15}---a linear concurrent $\lambda$-calculus.
Session-typed concurrent $\lambda$-calculus and $\pi$-calculus satisfy communication safety and session fidelity, namely that communication proceeds without any type mismatch of the data being transmitted and follows the predefined protocol specified by a session type.
Another key property in a concurrent setting is deadlock freedom, stating that agents communicate without getting stuck in cyclic dependencies. Unfortunately, deadlock freedom is a more involving property and session types alone are not enough to rule out deadlocks in cyclic structures of multiple interleaved sessions. Several techniques have been developed to address deadlock freedom in the $\pi$-calculus and concurrent $\lambda$-calculus with session types.

@@

With regards to GV, the original work on session types in GV~\cite{gayvasconcelos10,gayvasconcelos12} did not satisfy deadlock freedom. Later on, calculi in the GV family~\cite{wadler15,lindleymorris15} have achieved deadlock freedom via a syntactic restriction, \ie by combining channel creation and thread spawning into a single operation, called fork. The fork construct is the term representation of the cut construct in CP, which evaluates to a channel restriction combined with a parallel composition. Unfortunately, as with CP, this is restrictive as it limits communication structures to trees. There are several benefits of working with a functional language as opposed to name-passing calculi. Functional languages support higher-order functions, and have a capability for abstraction not usually present in process calculi. Working within a functional language allows to derive extensions of the communication capabilities of the language via well-understood extensions of the functional fragment, \ie deriving internal/external choice via sum types. Finally, in concurrent functional calculi, there is a clear separation between a program that the user writes, and a configuration, which is the state of a system as it evaluates. In process calculi, these are conflated.
Moreover, the benefit of working with GV over other session-typed functional languages is that GV has strong ties to linear logic, via its relation to CP~\cite{wadler12}, and consequently it has strong formal properties, \eg deadlock freedom, albeit in a restrictive way.
Following the above observations, we aim to further investigate GV and deadlock freedom, and thus we pose our research question:

### 2021-01-05 priority-cp.tex
Processed minor comments and inserted unresolved comments as todo notes.

We present an updated version of Priority CP (PCP)~\cite{dardhagay18}, which is Wadler's CP~\cite{wadler12} with {priorities}, and a translation from PCP to PGV.
The main difference with respect to PCP~\cite{dardhagay18} is removing commuting conversions and using structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all $\beta$-reductions that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them. %They show this by decomposing the reduction relation for CP into two phases: first, all $\beta$-reductions are performed, and second, commuting conversions are used to bring one particular action to the front, to eliminate the top-level cut.

>>>>

We present an updated version of Priority CP (PCP)~\cite{dardhagay18}, which is Wadler's CP~\cite{wadler12} with {priorities}, and a translation from PCP to PGV.
\todo{This one is a bit difficult to understand without context: in [14] it appears inside a typed semantics context, where changing dynamically priorities make sense. This is quite different from what is presented here. ({It would certainly be prudent of us that we do not need to dynamically change priorities in the updated version.})}
The main difference with respect to PCP~\cite{dardhagay18} is removing commuting conversions and using structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all $\beta$-reductions that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them. %They show this by decomposing the reduction relation for CP into two phases: first, all $\beta$-reductions are performed, and second, commuting conversions are used to bring one particular action to the front, to eliminate the top-level cut.
